analysis

### 2019-12-30 03_Preliminary_analysis.Rmd
Rainfall review done

```{r }

ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu")

ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu")

source("R/AUS_rainfall_function.r")
source("R/rainfall_sum_dat.R")

for(i in rain_dat_sum$trial_ref){
dat_rain <- rain_dat_sum[rain_dat_sum$trial_ref == i,]

   rain_dat_sum[which(rain_dat_sum$trial_ref == i), "rainfall_sum"] <- 
      AUS_rainfall(StartDate = as.Date(dat_rain$planting_date) +
                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "start_day"],
                EndDate = as.Date(dat_rain$planting_date) +
                   lm_rain[which(lm_rain$lm_adj_rsquared == max(lm_rain$lm_adj_rsquared)), "end_day"],
                latlong = as.vector(unlist(dat_rain[, 5:6])))
}

rain_lm <- lm(rainfall_sum ~ grain_yield, 
                             data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])

summary(rain_lm)

rain_dat_sum %>%
   ggplot(aes(x = grain_yield, y = rainfall_sum, colour = location))+
   geom_point() + 
   geom_abline(intercept = -167.98, slope = 284.44, colour = "red")

resid_rain_lm <- residuals(rain_lm)

>>>>

```{r rainLMrsquared}
ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared))+
   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu") 
```

```{r rainLMadjrsquared}
ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_adj_rsquared))+
   geom_raster(aes(fill = lm_adj_rsquared), interpolate = TRUE)+
   geom_contour(bins = 15, colour = "white")+
   geom_abline(intercept = 0, slope = 1, colour = "red")+
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)),], aes(x = start_day, y = end_day), colour =" red")+
   scale_fill_distiller(palette ="RdBu") 
```
